Titeln på avhandlingens språk

### 2022-08-31 model.tex
algorithm

The results of this processing on the samples from \cref{tab:data:exectime} can be seen in \cref{tab:data:exectime:processed}.
Three examples of the effect of this discretization and processing on the data are also presented in \cref{fig:timing}.

@@

@@

% \begin{algorithm}
%     \caption{Timing model algorithm}
%     \KwIn{%
%         \begin{itemize}
%             \item $T_\text{start}$: start timestamp of the previous step.
%             \item $T_\text{success}$: capture timestamp of the succesful sample of the previous step.
%             \item $T_\text{end}$: end timestamp of the previous step.
%             \item $t_\text{exec}$: execution time (in seconds) of the previous step.
%         \end{itemize}%
%     }
%     \KwOut{$t_\text{exec}'$: execution time for the current step.}

%     \Comment{%
%         Initial values:\\
%         $d \leftarrow 0$\\
%         $I_\text{prev} \leftarrow \text{NULL}$
%     }
%     $t_\text{wait} \leftarrow T_\text{success} - (T_\text{start} + t_\text{exec})$\;
%     $t_\text{round-trip} \leftarrow T_\text{end} - T_\text{success}$\;
%     $i \leftarrow t_\text{wait} + t_\text{round-trip}$ \Comment*[r]{raw impairment}
%     $I \leftarrow \text{BIN}(i)$ \Comment*[r]{bin impairment into\\discrete levels}

%     \If{$I_\text{prev} == \text{NULL}$}{%
%         $d \leftarrow 1$\;
%         $T \leftarrow \text{NO TRANSITION}$\;
%     } \ElseIf{$I_\text{prev} < I$}{%
%         $d \leftarrow 1$\;
%         $T \leftarrow \text{LOWER TO HIGHER} $
%     } \ElseIf{$I_\text{prev} > I$}{%
%         $d \leftarrow 1$\;
%         $T \leftarrow \text{HIGHER TO LOWER} $  
%     }

% \end{algorithm}

>>>>

The results of this processing on the samples from \cref{tab:data:exectime} can be seen in \cref{tab:data:exectime:processed}.
Three examples of the effect of this discretization and processing on the data are also presented in \cref{fig:timing}.
Finally, in \cref{alg:timings} we present a step-by-step breakdown of how this data is subsequently used to generate realistic execution times.
In plain English, a model which uses this processed data to generate execution times needs to maintain variables for duration, previous impairment, and most recent transition.
At the beginning of each step, the model
\begin{enumerate}
    \item Checks whether any change in impairment has occurred.
    If it has, it resets duration to \num{1} and updates the transition variable accordingly.
    If not, it increases the duration variable by one unless that increase causes it to exceed the threshold of steps required to forget a transition.
    If that's the case, instead the model resets duration to \num{1} and sets the transition variable to ``no transition''.
    \item Discretizes the updated duration value.
    \item Finds all samples with binned neuroticism, impairment, duration, and transition values matching the current state of the system.
    \item Randomly samples the filtered data to obtain a realistic execution time value.
    \begin{itemize}
        \item Alternatively, a distribution can be first be fitted to the filtered samples.
        The model then samples the theoretical distribution instead of the empirical samples.
    \end{itemize}
    \item Finally, updates the stored impairment value with the new impairment and proceeds to the next step.
\end{enumerate}

\begin{algorithm}
    \caption{Generating realistic execution times}\label{alg:timings}

    \SetKwInput{KwState}{Initial State}

    \KwIn{$\tau$: \ac{TTF} of the previous step.}
    \KwOut{$t_\text{exec}$: next execution time.}
    \KwState{%
        \begin{itemize}
            \item Binned neuroticism $N$.
            \item Number of steps to remember transitions for: $\delta \leftarrow 8$.
            \item Duration counter: $d \leftarrow 0$.
            \item Previous impairment: $I' \leftarrow \varnothing$.
            \item $B_\text{TTF}$ and $B_\text{duration}$ are functions for binning \ac{TTF} and duration into discrete levels, respectively.
            \item $F_\text{data}$ is a function which filters the data and returns only execution time samples which match the given levels of binned neuroticism, binned impairment, binned duration, and transition label.
        \end{itemize}
    }

    $I \leftarrow B_\text{TTF}(\tau)$ \tcc*{discretize \ac{TTF}}

    \uIf{($I' == \varnothing$) {\normalfont\textbf{or}}\\\hspace{1em}($T \neq \text{``NO TRANSITION''}$ {\normalfont\textbf{and}} $d + 1 > \delta$)}{%
        $d \leftarrow 1$\;
        $T \leftarrow \text{``NO TRANSITION''}$\;
    } \uElseIf{$I' < I$}{%
        $d \leftarrow 1$\;
        $T \leftarrow \text{``LOWER TO HIGHER''} $
    } \uElseIf{$I' > I$}{%
        $d \leftarrow 1$\;
        $T \leftarrow \text{``HIGHER TO LOWER''} $  
    } \Else {%
        $d \leftarrow d + 1$\;
    }
    $I' \leftarrow I$ \tcc*{store impairment for later}
    $D \leftarrow B_\text{duration}(d)$ \tcc*{discretize duration}

    \tcc{next, filter the data to select only the matching samples}
    $E \leftarrow F_\text{data}(N, I, D, T)$ \;
    \tcc{finally, sample the data to return a realistic execution time}
    $t_\text{exec} \leftarrow {SAMPLE}(E)$\;

\end{algorithm}

@@

\subsection{Generating realistic samples}

@@
